PAQ for parenting observational study

### 2017-05-31 paq/parenting_obs_paq.Rmd
updated analysis for JA

ggplot(atts_m, aes(x = category, y = mean)) + 
  geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9))
```
```{r}
dq$parent_ed <- as.factor(dq$parent_ed)

>>>>

ggplot(atts_m, aes(x = category, y = mean)) + 
  geom_bar(stat="identity") + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
             position = position_dodge(width = .9))
```

Demographics
```{r}
dq$parent_ed <- as.factor(dq$parent_ed)
